### 2025-05-28 Paper.tex
Added files

%% This is file `sample-sigconf-authordraft.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `all,proceedings,bibtex,authordraft')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf-authordraft.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%% The first command in your LaTeX source must be the \documentclass
%% command.
%%
%% For submission and review of your manuscript please change the
%% command to \documentclass[manuscript, screen, review]{acmart}.
%%
%% When submitting camera ready or to TAPS, please change the command
%% to \documentclass[sigconf]{acmart} or whichever template is required
%% for your publication.
%%
%%
\documentclass[sigconf,authordraft]{acmart}
\usepackage{float}
\usepackage{placeins}
\title{Post CMOS technologies: An Overview and Analysis}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmlicensed}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{XXXXXXX.XXXXXXX}
%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Conference acronym 'XX]{Make sure to enter the correct
  conference title from your rights confirmation email}{June 03--05,
  2018}{Woodstock, NY}
%%
%%  Uncomment \acmBooktitle if the title of the proceedings is different
%%  from ``Proceedings of ...''!
%%
%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
%%  June 03--05, 2018, Woodstock, NY}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% For managing citations, it is recommended to use bibliography
%% files in BibTeX format.
%%
%% You can then either use BibTeX with the ACM-Reference-Format style,
%% or BibLaTeX with the acmnumeric or acmauthoryear sytles, that include
%% support for advanced citation of software artefact from the
%% biblatex-software package, also separately available on CTAN.
%%
%% Look at the sample-*-biblatex.tex files for templates showcasing
%% the biblatex styles.
%%

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Post CMOS technologies: An Overview and Analysis}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Willson Luo}
\email{willsonluo@ucla.edu}
\affiliation{
  \institution{University of California Los Angeles}
  \city{Los Angeles}
  \state{California}
  \country{USA}
}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  The rapid evolution of computing is pushing the limits of traditional 
  silicon-based electronics, necessitating the exploration of 
  novel materials and architectural paradigms. This paper 
  investigates three transformative technologies poised to 
  redefine future computational systems: Carbon Nanotubes 
  (CNTs), Spintronics, and Memristors. We explore how Carbon 
  Nanotube Field-Effect Transistors (CNFETs) offer enhanced 
  performance and energy efficiency by enabling scaling beyond 
  conventional limits, exemplified by the development of 
  sophisticated CNFET-based microprocessors. Concurrently, 
  Spintronics, particularly through Magnetoelectric Spin-Orbit 
  (MESO) devices, promises ultra-low power logic by leveraging 
  electron spin, introducing innovative concepts like majority 
  logic gates. Furthermore, we examine Memristors, which address 
  the Von Neumann bottleneck by integrating memory and processing, 
  facilitating advanced applications in neuromorphic and analog 
  computing, as demonstrated by their use in artificial neural 
  networks and threshold logic gates. While each technology 
  presents unique challenges in fabrication and integration, 
  their distinct advantages offer compelling pathways toward 
  building faster, smaller, and more energy-efficient computing 
  systems for the next generation.
  CMOS.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Do, Not, Us, This, Code, Put, the, Correct, Terms, for,
  Your, Paper}
%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
The pursuit of faster, smaller, and more energy-efficient computing
has been a driving force for technological advancement since the 
creation of the transistor. For decades, CMOS (Complementary
metal-oxide-semiconductor) technology has served as the foundation 
of of the modern computer. However, as we continue to approve our 
transistors and approach fundamental limits, the need for novel 
paradigms becomes increasinly urgent. This paper explores three 
technologies that could shape the future of computing: Carbon Nanotubes
(CNTs), Spintronics, and Memristors. Each offers their own 
advantages that address the limitations of silicon transistors,
varying from faster performance to significantly reduced power 
consumption.

Carbon Nanotubes, with their exceptional electrical and thermal 
properties, present a compelling alternative to silicon in 
field-effect transistors (FETs). The ability to scale devices 
beyond current limits, coupled with high carrier mobility and 
superior heat dissipation, positions Carbon Nanotube FETs (CNFETs) 
as a potential successor for high-performance, low-power logic. 
Recent advancements, such as the development of the RV16X-NANO 
microprocessor at MIT, demonstrate the practical viability of 
CNFET-based computing, showcasing their compatibility with 
existing design methodologies and their ability to execute 
complex instructions.

Beyond simply replacing silicon, Spintronics offers a 
revolutionary approach to information processing by leveraging 
the intrinsic spin of electrons in addition to their charge. 
Magnetoelectric Spin-Orbit (MESO) devices, a key development in 
spintronics, promise ultra-low power logic operations by directly 
coupling electron spin with its movement and enabling control 
through both electrical and magnetic properties. These devices 
offer superior switching energy, lower operating voltages, and 
enhanced logic density, with the potential to implement universal 
logic through majority gates, fundamentally transforming how logic 
functions are conceived and executed.

Finally, Memristors, often described as the "fourth fundamental 
circuit element," introduce a new dimension to computing by 
combining memory and processing capabilities within a single 
device. This integration directly addresses the Von Neumann 
bottleneck, the traditional separation of memory and logic that 
limits computational speed and efficiency. Memristor-based 
threshold logic gates and crossbar arrays hold immense promise 
for neuromorphic and analog computing, enabling highly efficient 
Vector-Matrix Multiplication (VMM) crucial for artificial neural 
networks. While challenges in manufacturing reliability and 
programmability persist, the ability of memristors to store 
multiple bits and their non-volatile nature offer a path toward 
more compact, power-efficient, and brain-inspired computing 
architectures.

This paper will delve into the principles, advancements, and 
challenges associated with each of these transformative technologies, 
highlighting their individual contributions and their collective 
potential to shape the next generation of computing systems.

\section{Carbon Nanotubes (CNTs) for Advanced Electronics}
As the semiconductor continues its pursuit of miniaturization 
and greater performance, the fundamental limits of silicon-based 
transistors become increasingly apparent. This fundamental limit to 
the scaling of traditional transistors has given rise to many 
alternatives among them being Carbon Nanotubes (CNTs), one 
dimensional nanostructures that possess a unique combination of 
characteristics making them highly attractive for advancing 
electronics.

CNTs are composed of graphene sheets rolled into cylindrical tubes
with their structure determining whether they behave as
semiconductors or metals. his tunable electrical property,
coupled with their nanoscale dimensions, 
high carrier mobility, and exceptional thermal conductivity, 
positions CNTs as a compelling material for high-performance 
computing. Their inherent flexibility also opens avenues for 
novel applications beyond traditional rigid electronics. 
This section will delve into the fundamental properties of 
CNTs, explore their application in Carbon Nanotube Field-Effect 
Transistors (CNFETs), highlight recent advancements that 
demonstrate their potential, and discuss the significant 
fabrication challenges that must be overcome for their widespread 
adoption.

\subsection{Fundamental Properties of Carbon Nanotubes}
Carbon nanotubes are made of an allotrope of carbon known as 
graphene.

Their structure can be characterized into to major types.
Single-walled and multi-walled carbon nanotubes. Single-walled 
carbon nanotubes consist of a single graphene sheet rolled into 
a cylinder typically with a diameter between 0.5 to 2.0 
nanometers. Multi-walled carbon nanotubes are comprised of 
multiple concentric graphene cylinders nested within each other. 
Their diameter can extend up to tens of nanometers.

The electrical properties can also vary depending on the structure 
and chirality (the angle at which the graphene sheet
is rolled up) of the CNTs. This means that a CNT can behave either 
as metals with a high conductivity or semiconductors making them 
suitable for making transistors.

CNTs also have extremely high thermal conductivity making them
suitable to overcome many of the power limitations of current 
CMOS scaling.

Finally, CNTs are among the strongest and stiffest materials 
known, possessing exceptional tensile strength and elastic 
modulus. Moreover, they are remarkably flexible, capable of 
withstanding considerable mechanical strain without fracturing. 
This flexibility is particularly advantageous for emerging 
flexible electronics and 3D integration.

\subsection{Carbon Nanotube Field Effect Transistors (CNFETs)}
The ability of semiconductor CNTs to conduct extremely effectively 
and their nanoscale dimensions make them ideal candidates for 
making the channel in field effect transistors. These properties 
allow CNFETs to offer several significant advantages over silicon 
based FETs:
\begin{itemize}
  \item Aggressive Scaling: Their nanoscale dimensions allow for
  device scaling below the 5 nanometer limit.
  \item High Carrier Mobility: The ballistic or near-ballistic 
  transport of carriers within CNTs leads to very high carrier
  mobility, which translates directly to faster switching speeds 
  and improved device performance.
  \item Lower Power Consumption: CNFETs can operate effectively 
  at lower voltages due to their superior electrical 
  characteristics, resulting in significantly reduced power 
  dissipation.
  \item Enhanced Gate Control: As one-dimensional materials, 
  CNTs offer excellent electrostatic control by the gate, 
  leading to lower off-state currents and steeper subthreshold 
  swings.
  \item Superior Thermal Management: Their high thermal 
  conductivity facilitates efficient heat dissipation, 
  mitigating hot spots and improving reliability in densely 
  packed circuits.
  \item Material Flexibility: The mechanical flexibility of CNTs 
  enables the development of bendable electronics and facilitates 
  potential three-dimensional chip stacking and integration, 
  offering new avenues for compact and innovative designs.
\end{itemize}

\begin{figure}[h]
  \centering
  \includegraphics[width = \linewidth]{images/Screenshot 2025-05-26 at 8.51.02 PM.png}
  \caption{Diagram of CNFET as combination of MOSFET and FinFET}
\end{figure}

\subsection{Logic Operations}
Since CNFETs operate just like normal transistors their integration 
into creating logic gates is the exact same as a traditional 
transistor. They still follow CMOS architecture and their benefits 
come from their performance advantage compared to traditional transistors rather than 
new operating paradigms.

\subsection{Recent Advancements: RV16X-NANO Microprocessor}
The RV16X-NANO Microprocessor has been one of the biggest advancements 
in making a computer with CNFETs. The MIT Medical Electronic Device 
Realization Center were able to develop a 16 bit nanoprocessor which
they named RV16X-NANO. The microprocessor was built of the RISC-V
instruction set which was written through Bluespec and then compiled 
into Verilog, an RTL hardware description langauge. The microprocessor 
was comprised of over 14000 CMOS CNFETs that were made using more than 
10 million CNTs.

On this microprocessor they were able to implement many standard logic 
blocks like multiplexers, arithmetic logic units, decoders, and encoders. 
Most notably, they were able to execute the famous "Hello World"
program.

\begin{figure}
  \centering
  \includegraphics[width = \linewidth]{images/Screenshot 2025-05-26 at 8.56.27 PM.png}
  \caption{Architecture and Design of RV16X-NANO}
\end{figure}

\subsection{Challenges in CNFET Fabrication and Integration}
Despite the considerable amount of progress made, several challenges 
still need to be addressed before CNFETs can achieve widespread 
viability and meet yield requirements for very large scale integration
(VLSI). Most signficantly, material and manufacturing defects are 
the current biggest challenge. Current methods of CNT fabrication 
lack a reliable way of controlling the chirality leading to many
CNTs exhibiting metallic properties instead of being semiconductors. 
Even after achieving semiconducting CNTs, manufacturing processes still
introduce defects and variability across a wafer. This includes variation
in CNFET density and contact resistance leading to non uniform performance
across an entire chip. In addition to manufacturing issues there 
still lacks a way of seamlessly integrating with traditional silicon
CMOS components. Overcoming these challenges is crucial to achieving

\section{Spintronics: Beyond Charge-Based Computing}
Traditional electronics primarily rely on the charge of electrons 
to process and store information. 1s and 0s are coded by high and 
low volages which are determined by electric fields created by
distributions of charges. However, this approach faces inherent 
limitations in terms of power consumption and switching speed as 
devices continue to shrink. Spintronics emerges as a new paradigm 
that seeks to overcome these limitations by exploiting not only electron's 
charge but also its intrinsic angular momentum, known as spin. 
This additional degree of freedom offers the potential for 
fundamentally new device functionalities, leading to 
ultra-low power consumption, higher operating speeds, and increased 
logic density.

\subsection{Introduction to Spintronics}
Spintronics is the study and exploitation of the spin 
of electrons in solid-state devices. Unlike charge, which is a 
scalar quantity, spin is a quantum mechanical property that can 
be oriented in different directions (e.g., "spin-up" or "spin-down").
This allows for the encoding of information in a non-volatile magnetic
state. The promise of spintronics lies in its ability to enable 
novel functionalities and overcome the inherent energy dissipation 
associated with moving charges in conventional electronics. By manipulating 
spin currents and magnetic states, spintronic devices aim to perform logic 
operations with significantly reduced energy footprints.

\subsection{Magnetoelectric Spin-Orbit (MESO) Devices}

\section{Memristors}

\section{Comparative Analysis}

\section{Conclusion}

\section{Acknowledgments}

Authors of any work published by ACM will need to complete a rights
form. Depending on the kind of work, and the rights management choice
made by the author, this may be copyright transfer, permission,
license, or an OA (open access) agreement.

Regardless of the rights management choice, the author will receive a
copy of the completed rights form once it has been submitted. This
form contains \LaTeX\ commands that must be copied into the source
document. When the document source is compiled, these commands and
their parameters add formatted text to several areas of the final
document:
\begin{itemize}
\item the ``ACM Reference Format'' text on the first page.
\item the ``rights management'' text on the first page.
\item the conference information in the page header(s).
\end{itemize}

Rights information is unique to the work; if you are preparing several
works for an event, make sure to use the correct set of commands with
each of the works.

The ACM Reference Format text is required for all articles over one
page in length, and is optional for one-page articles (abstracts).

\section{CCS Concepts and User-Defined Keywords}

Two elements of the ``acmart'' document class provide powerful
taxonomic tools for you to help readers find your work in an online
search.

The ACM Computing Classification System ---
\url{https://www.acm.org/publications/class-2012} --- is a set of
classifiers and concepts that describe the computing
discipline. Authors can select entries from this classification
system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
commands to be included in the \LaTeX\ source.

User-defined keywords are a comma-separated list of words and phrases
of the authors' choosing, providing a more flexible way of describing
the research being presented.

CCS concepts and user-defined keywords are required for for all
articles over two pages in length, and are optional for one- and
two-page articles (or abstracts).

\section{Sectioning Commands}

Your work should use standard \LaTeX\ sectioning commands:
\verb|\section|, \verb|\subsection|, \verb|\subsubsection|,
\verb|\paragraph|, and \verb|\subparagraph|. The sectioning levels up to
\verb|\subsusection| should be numbered; do not remove the numbering
from the commands.

Simulating a sectioning command by setting the first word or words of
a paragraph in boldface or italicized text is {\bfseries not allowed.}

Below are examples of sectioning commands.

\subsection{Subsection}
\label{sec:subsection}

This is a subsection.

\subsubsection{Subsubsection}
\label{sec:subsubsection}

This is a subsubsection.

\paragraph{Paragraph}

This is a paragraph.

\subparagraph{Subparagraph}

This is a subparagraph.

\section{Tables}

The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
high-quality tables.

Table captions are placed {\itshape above} the table.

Because tables cannot be split across pages, the best placement for
them is typically the top of the page nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and the
table caption.  The contents of the table itself must go in the
\textbf{tabular} environment, to be aligned properly in rows and
columns, with the desired horizontal and vertical rules.  Again,
detailed instructions on \textbf{tabular} material are found in the
\textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table~\ref{tab:freq} is included in the input file; compare the
placement of the table here with the table in the printed output of
this document.

\begin{table}
  \caption{Frequency of Special Characters}
  \label{tab:freq}
  \begin{tabular}{ccl}
    \toprule
    Non-English or Math&Frequency&Comments\\
    \midrule
    \O & 1 in 1,000& For Swedish names\\
    $\pi$ & 1 in 5& Common in math\\
    \$ & 4 in 5 & Used in business\\
    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
  \bottomrule
\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of the page's
live area, use the environment \textbf{table*} to enclose the table's
contents and the table caption.  As with a single-column table, this
wide table will ``float'' to a location deemed more
desirable. Immediately following this sentence is the point at which
Table~\ref{tab:commands} is included in the input file; again, it is
instructive to compare the placement of the table here with the table
in the printed output of this document.

\begin{table*}
  \caption{Some Typical Commands}
  \label{tab:commands}
  \begin{tabular}{ccl}
    \toprule
    Command &A Number & Comments\\
    \midrule
    \texttt{{\char'134}author} & 100& Author \\
    \texttt{{\char'134}table}& 300 & For tables\\
    \texttt{{\char'134}table*}& 400& For wider tables\\
    \bottomrule
  \end{tabular}
\end{table*}

Always use midrule to separate table header rows from data rows, and
use it only for this purpose. This enables assistive technologies to
recognise table headers and support their users in navigating tables
more easily.

\section{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of the three are
discussed in the next sections.

\subsection{Inline (In-text) Equations}
A formula that appears in the running text is called an inline or
in-text formula.  It is produced by the \textbf{math} environment,
which can be invoked with the usual
\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
and structures, from $\alpha$ to $\omega$, available in
\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
examples of in-text equations in context. Notice how this equation:
\begin{math}
  \lim_{n\rightarrow \infty}x=0
\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsection{Display Equations}
A numbered display equation---one set off by vertical space from the
text and centered horizontally---is produced by the \textbf{equation}
environment. An unnumbered display equation is produced by the
\textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols and
structures available in \LaTeX\@; this section will just give a couple
of examples of display equations in context.  First, consider the
equation, shown as an inline equation above:
\begin{equation}
  \lim_{n\rightarrow \infty}x=0
\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}
  \sum_{i=0}^{\infty} x + 1
\end{displaymath}
and follow it with another numbered equation:
\begin{equation}
  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\section{Figures}

The ``\verb|figure|'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown
in the example below.
\begin{figure}[h]
  \centering
%   \includegraphics[width=\linewidth]{sample-franklin}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{A woman and a girl in white dresses sit in an open car.}
\end{figure}

Your figures should contain a caption which describes the figure to
the reader.

Figure captions are placed {\itshape below} the figure.

Every figure should also have a figure description unless it is purely
decorative. These descriptions convey what’s in the image to someone
who cannot see it. They are also used by search engine crawlers for
indexing images, and when images cannot be loaded.

A figure description must be unformatted plain text less than 2000
characters long (including spaces).  {\bfseries Figure descriptions
  should not repeat the figure caption – their purpose is to capture
  important information that is not already provided in the caption or
  the main text of the paper.} For figures that convey important and
complex new information, a short text description may not be
adequate. More complex alternative descriptions can be placed in an
appendix and referenced in a short figure description. For example,
provide a data table capturing the information in a bar chart, or a
structured list representing a graph.  For additional information
regarding how best to write figure descriptions and why doing this is
so important, please see
\url{https://www.acm.org/publications/taps/describing-figures/}.

\subsection{The ``Teaser Figure''}

A ``teaser figure'' is an image, or set of images in one figure, that
are placed after all author and affiliation information, and before
the body of the article, spanning the page. If you wish to have such a
figure in your article, place the command immediately before the
\verb|\maketitle| command:
\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}

\section{Citations and Bibliographies}

The use of \BibTeX\ for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.

The bibliography is included in your source document with these two
commands, placed just before the \verb|\end{document}| command:
\begin{verbatim}
  \bibliographystyle{ACM-Reference-Format}
  \bibliography{bibfile}
\end{verbatim}
where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
suffix, of the \BibTeX\ file.

Citations and references are numbered by default. A small number of
ACM publications have citations and references formatted in the
``author year'' style; for these exceptions, please include this
command in the {\bfseries preamble} (before the command
``\verb|\begin{document}|'') of your \LaTeX\ source:
\begin{verbatim}
  \citestyle{acmauthoryear}
\end{verbatim}

  Some examples.  A paginated journal article \cite{Abril07}, an
  enumerated journal article \cite{Cohen07}, a reference to an entire
  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
  monograph/whole book in a series (see 2a in spec. document)
  \cite{Harel79}, a divisible-book such as an anthology or compilation
  \cite{Editor00} followed by the same example, however we only output
  the series if the volume number is given \cite{Editor00a} (so
  Editor00a's series should NOT be present since it has no vol. no.),
  a chapter in a divisible book \cite{Spector90}, a chapter in a
  divisible book in a series \cite{Douglass98}, a multi-volume work as
  book \cite{Knuth97}, a couple of articles in a proceedings (of a
  conference, symposium, workshop for example) (paginated proceedings
  article) \cite{Andler79, Hagerup1993}, a proceedings article with
  all possible elements \cite{Smith10}, an example of an enumerated
  proceedings article \cite{VanGundy07}, an informally published work
  \cite{Harel78}, a couple of preprints \cite{Bornmann2019,
    AnzarootPBM14}, a doctoral dissertation \cite{Clarkson85}, a
  master's thesis: \cite{anisi03}, an online document / world wide web
  resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game
  (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05}
  and (Case 3) a patent \cite{JoeScientist001}, work accepted for
  publication \cite{rous08}, 'YYYYb'-test for prolific author
  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
  contain 'duplicate' DOI and URLs (some SIAM articles)
  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
  couple of citations with DOIs:
  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}.
  Artifacts: \cite{R} and \cite{UMassCitations}.

\section{Acknowledgments}

Identification of funding sources and other support, and thanks to
individuals and groups that assisted in the research and the
preparation of the work should be included in an acknowledgment
section, which is placed just before the reference section in your
document.

This section has a special environment:
\begin{verbatim}
  \begin{acks}
  ...
  \end{acks}
\end{verbatim}
so that the information contained therein can be more easily collected
during the article metadata extraction phase, and to ensure
consistency in the spelling of the section heading.

Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.

\section{Appendices}

If your work needs an appendix, add it before the
``\verb|\end{document}|'' command at the conclusion of your source
document.

Start the appendix with the ``\verb|appendix|'' command:
\begin{verbatim}
  \appendix
\end{verbatim}
and note that in the appendix, sections are lettered, not
numbered. This document has two appendices, demonstrating the section
and subsection identification method.

\section{Multi-language papers}

Papers may be written in languages other than English or include
titles, subtitles, keywords and abstracts in different languages (as a
rule, a paper in a language other than English should include an
English title and an English abstract).  Use \verb|language=...| for
every language used in the paper.  The last language indicated is the
main language of the paper.  For example, a French paper with
additional titles and abstracts in English and German may start with
the following command
\begin{verbatim}
\documentclass[sigconf, language=english, language=german,
               language=french]{acmart}
\end{verbatim}

The title, subtitle, keywords and abstract will be typeset in the main
language of the paper.  The commands \verb|\translatedXXX|, \verb|XXX|
begin title, subtitle and keywords, can be used to set these elements
in the other languages.  The environment \verb|translatedabstract| is
used to set the translation of the abstract.  These commands and
environment have a mandatory first argument: the language of the
second argument.  See \verb|sample-sigconf-i13n.tex| file for examples
of their usage.

\section{SIGCHI Extended Abstracts}

The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
not in Word) produces a landscape-orientation formatted article, with
a wide left margin. Three environments are available for use with the
``\verb|sigchi-a|'' template style, and produce formatted output in
the margin:
\begin{description}
\item[\texttt{sidebar}:]  Place formatted text in the margin.
\item[\texttt{marginfigure}:] Place a figure in the margin.
\item[\texttt{margintable}:] Place a table in the margin.
\end{description}

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\section{Research Methods}

\subsection{Part One}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
lacinia dolor. Integer ultricies commodo sem nec semper.

\subsection{Part Two}

Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
eros. Vivamus non purus placerat, scelerisque diam eu, cursus
ante. Etiam aliquam tortor auctor efficitur mattis.

\section{Online Resources}

Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
enim maximus. Vestibulum gravida massa ut felis suscipit
congue. Quisque mattis elit a risus ultrices commodo venenatis eget
dui. Etiam sagittis eleifend elementum.

Nam interdum magna at lectus dignissim, ac dignissim lorem
rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
massa et mattis lacinia.

\end{document}
\endinput
%%
%% End of file `sample-sigconf-authordraft.tex'.

### 2025-05-28 Paper.tex
new text

@@
 operations with significantly reduced energy footprints. 
+By also utilizing using a charge as well as spin this gives the potential to encode more 
+states where there can be a combination of high or low voltage along 
+with up or down spin.
 
 \subsection{Magnetoelectric Spin-Orbit (MESO) Devices} 
+One promising way to compute and perform logic using spintronics is 
+Magnetoelectric Spin-Orbit (MESO). In this scheme binary is represented 
+in the up or down spin state of a nanomagnet. These devices rely 
+on 2 major physical effects. The first is spin-orbit transduction where 
+if a current flows through a material with a strongly coupled spin 
+the current will also gain that spin. The second effect is magnetoelectric 
+switching where you can control a materials magnetic properties by applying 
+an electric field. For instance switching the spin state with the help of 
+an electric field.
+
+\subsubsection{Principle of Operation}
+An input logic is provided through a voltage and electric field which 
+will set the magnetization in a magnet to be in a certain direction. This 
+converts an electrical input into a magnetic state where the spin state 
+can now be used to represent the binary 0 or 1.
+
+To then generate an output a current is injected into the nanomagnet 
+which will cause the output current from the nanomagnet to all have 
+the same
 

### 2025-05-28 Paper.tex
memristors

@@
 \section{Memristors}
+The Von Neumann architecture, which physically separates the processing 
+unit from the memory has been the preferred method for making computers. 
+However, as our chips become faster bottlenecks from I/O also come up 
+where information can't be moved to and from the chip fast enough. Memristors, 
+first described as the fourth missing circuit element, offer a way 
+to link memory and compute in a single device. This combination opens up
+potential for more efficient brain inspired computing, particularly 
+in the neuromorphic and analog world.
+
+\subsection{The Memristor Concept}
+A memristor, combination of the words memory and resistor, is a device 
+that can have a programmble resistance. It was often described as 
+the fourth circuit element because it was believed that magnetic fields 
+could be used to change the resistance of these devices. However, recent 
+devices don't rely on magnetic fields at all and instead use electric fields 
+to change the physical and chemical properties of these devices to program 
+the resistance. This property, where it can "remember" its resistance allows 
+for non volatile memory and reconfigurable logic without having to change 
+the physical connections on a chip.
+
+In addition to these new computing regimes they also offer advantages 
+in several other areas. They can be manufactured into nanoscale 
+dimensions below those of a silicon transistor allowing for greater scaling 
+and higher density integration. Their ability to store memory even 
+when power is switched enables lower power consumption. Since they can 
+also be programmed into continuous resistance values they have the 
+ability to store more than just 1 bit per device. Recent experiments
+have shown one memristor being able to store 5-7 bits. Advances 
+in memristors have also demonstrated a high level of CMOS compatability 
+allowing them to be used in hybrid structures with traditional CMOS 
+devices.
+
+\subsection{Memristor Based Threshold Logic Gate (TLG)}
+Beyond their abilities to store memory, memristors are perfectly suited 
+for implementing threshold logic gates.
 

### 2025-06-03 Paper.tex
memristor section

@@
 
+\subsection{Personal Thoughts}
+Overall CNFETs seem like a very promising area where there could be 
+a lot of development. Since it doesn't deviate signficantly from 
+traditional transistors it can be implemented into already made 
+computing schemes making it more appealing for companies to invest 
+in. It is much more likely for top fabrication companies like 
+TSMC or Intel to look into CNFETs than some other technologies
+that present completely new computing paradigms. The progress made in 
+CNFETs has also been extremely promising as demonstrated by MIT's 
+RV16X-NANO computer. The milestone to already have demonstrated 
+such funcionality proves that this is a technology that is really 
+feasible for the future. Graphene is also an area that has a good 
+amount of research going into it so carbon nanotubes in general 
+are sure to get more attention.
+
+With new chips there is a greater emphasis on chiplet technology 
+as well as 3D integration. Again, CNFETs look very promising in that
+area. Along with that, the medical industry is also constantly looking 
+for flexible devices that can better interact with the human body 
+which is another area where CNFETs shine in.
+
+Though there are still some big hurdles to overcome in manufacturing 
+CNFETs at large scales and reliably I believe with just a few more 
+breakthroughs they can become quite mainstream where large amounts 
+of investments will be poured into CNFETs and accelerate their development 
+greatly.
+
 \section{Spintronics: Beyond Charge-Based Computing}
@@
 for implementing threshold logic gates.
+
+\subsection{Threshold Logic Gate}
+A threshold logic gate is a gate that outputs a high signal if 
+an input signal surpasses a certain threshold and outputs low 
+otherwise. To give an example simply, imagine the input had a range 
+of voltages from 0-9 and there is a threshold voltage of 5. Any
+input voltage above high will output a binary high signal from the 
+gate and any voltage below will output a low signal. A TLG 
+is oftentimes also used to analyze a weighted sum from its inputs 
+and see if that is above the threshold.
+
+With these characteristics a TLG can implement any linearly separable
+function. This means that for a given function, there exists a 
+dividing line (or hyperplane in higher dimensions) that would 
+separate all input combinations to one of two distinct output 
+groups.
+
+This also means that a single TLG can implement a boolean function 
+that would require multiple logic gates to realize. For example, a 
+majority gate would require at least 4 NAND gates to be realized in 
+traditional CMOS design while it can be implemented in just one TLG.
+
+\subsubsection{Memristor-Based Threshold Logic Gate}
+da
 

### 2025-06-04 Paper.tex
bibs
idk what changes i made

@@
 
-\subsection{Threshold Logic Gate}
+\subsubsection{Threshold Logic Gate}
 A threshold logic gate is a gate that outputs a high signal if 
@@
 \subsubsection{Memristor-Based Threshold Logic Gate}
-da
+Memristors are ideal for TLG implementation since their variable 
+resistance can act as programmable weights. A common architecture
+for a memristor based TLG implements a hybrid architecture with 
+memristors and traditional CMOS components into two main parts:
+a differential part and a sensor part.
+
+The differential part is where a memristor is actually used. Each 
+memristor is paired with a transistor known as a 1T1M array.
+Here an input and reference threshold signal is taken in. When a 
+voltage is then applied as the input current flows through the
+memristor. The memristor here acts as a knob that controls how much 
+current is passed through this differential part. This part 
+can also be switched off when not in use to save power.
+
+The current from the differential part then goes to the sensor. 
+The sensor compares a combined current coming from either one or 
+multiple differential parts and sees if its above the threshold. 
+Based on this comparison either a 1 or 0 is outputted indicating 
+whether the sum of the weights have surpassed the threshold. 
+%\cite here%
+
+\subsubsection{Challenges}
+Despite the theoretical efficiency of memristor based TLGs, 
+their practical implementation still face significant challenges. 
+Fabrication is still very difficult and there are no EDA tools 
+compatible with designing devices made of memristors TLGs.
+
+\subsection{Hardware Implementation of Memristor-Based Artificial Neural Networks}
+Beyond logic gates, memristors are particularly compelling for 
+neural networks due to their inherent ability to perform efficient 
+vector matrix multiplicaton which serves as the backbone of 
+modern neural networks.
 
@@
 \bibliographystyle{ACM-Reference-Format}
-\bibliography{sample-base}
+\bibliography{refs}
 

### 2025-06-05 Paper.tex
finished memristor facts

@@
 
+\subsubsection{Vector-Matrix Multiplication (VMM) Core}
+The central component in the vector-matrix multiplication core 
+is the memristor crossbar array. In this array, memrisotrs are placed
+at the crosspoints of a grid of wires. Voltages are inputted through
+the rows of the wire and the at each cross point the current is 
+found through Ohm's Law. Kirchoff's current law then sums up all the 
+currents through the vertical beams and the sum of these currents 
+is the result of the vector multiplication. Mathematically the
+product as a current is 
+\[I_j = \Sigma_iV_iG_{ij}.\]
+
+These raw analog values are then fed to a analog to digital converter
+(ADC) to then turn into digital magnitudes. Finally, an activation
+function (often a sigmoid or ReLU) is applied to these results to 
+introduce nonlinearities, making the output resemble various desired 
+distributions. 
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale = 0.3]{images/Neural-network-implementation-using-memristor-crossbar-arrays-a-shows-a-conventional.png}
+  \caption{Memristor crossbar array}
+\end{figure}
+
+\subsubsection{Demonstrations of Memristor Neural Networks}
+Notably, the University of Michigan created a memristor based 
+computer that utilized a 54x108 memristor crossbar array. 
+With this computer they were able to create a single layer perception 
+that classified a 5x5 array of pixels, identifying the greek letters 
+drawn in the 25 pixel array with 100\% accuracy. In addition, they 
+implemented a two layer neural network that found commonalities and 
+differences in breast cancer screenings, correctly classifying 
+the cases as benign or malignant with 94.6\% accuracy.
+%cite here%
+
+\subsection{Challenges to Implementing Memristors}
+Despite their demonstrated potential, several critical challenges still
+prevent the widespread and practical use of memristors. Among these challenges
+the most prominent ones are the lack of reliable manufacturing ability,
+resistance drift, and non-linear resistance programming.
+
+Memristors are still unable to be manufactured reliably and the 
+the cost of metal alloys is much more than that of silicon. Manufacturing 
+metals to these scales is also much harder. These manufactured devices also 
+suffer from drift where the programmed resistance can change over time 
+to deviations in the environment like temperature. Non-linearities 
+in how the resistance is programmed also make it extremely difficult to
+program large scale memristor arrays. Supposed identitical memristors 
+could require different voltage thresholds or to be applied for varying 
+amount of times to program them to have the same resistance.
+
+\subsection{Personal Thoughts}
+With the advent of
+
 \section{Comparative Analysis}

### 2025-06-13 Paper.tex
finished

@@
 %%
-\documentclass[sigconf,authordraft]{acmart}
+\documentclass[sigconf]{acmart}
 \usepackage{float}
@@
 \setcopyright{acmlicensed}
-\copyrightyear{2018}
-\acmYear{2018}
-\acmDOI{XXXXXXX.XXXXXXX}
+\copyrightyear{2025}
+\acmYear{2025}
 %% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[Conference acronym 'XX]{Make sure to enter the correct
-  conference title from your rights confirmation email}{June 03--05,
-  2018}{Woodstock, NY}
 %%
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{Do, Not, Us, This, Code, Put, the, Correct, Terms, for,
-  Your, Paper}
+\keywords{Post-CMOS Technology, Carbon Nanotubes, CNFETs, Spintronics, MESO Devices, 
+Memristors, Crossbar Array, In-Memory Computing, Vector Matrix Multiplication, Majority Gate,
+3D Integration, Threshold Logic, Analog Computing}
 %% A "teaser" image appears between the author and affiliation
@@
 This flexibility is particularly advantageous for emerging 
-flexible electronics and 3D integration.
+flexible electronics and 3D integration \cite{appenzeller2008carbon}.
 
@@
   potential three-dimensional chip stacking and integration, 
-  offering new avenues for compact and innovative designs.
+  offering new avenues for compact and innovative designs \cite{javey2003ballistic}.
 \end{itemize}
@@
   \includegraphics[width = \linewidth]{images/Screenshot 2025-05-26 at 8.51.02 PM.png}
-  \caption{Diagram of CNFET as combination of MOSFET and FinFET}
+  \caption{Diagram of CNFET as combination of MOSFET and FinFET (Image from \cite{appenzeller2008carbon})}
 \end{figure}
@@
 program.
+\cite{hills2019modern}
 
@@
   \includegraphics[width = \linewidth]{images/Screenshot 2025-05-26 at 8.56.27 PM.png}
-  \caption{Architecture and Design of RV16X-NANO}
+  \caption{Architecture and Design of RV16X-NANO (Image from \cite{hills2019modern})}
 \end{figure}
@@
 still lacks a way of seamlessly integrating with traditional silicon
-CMOS components. Overcoming these challenges is crucial to achieving
+CMOS components\cite{hills2019modern}.
+Overcoming these challenges is crucial to achieving reliable CNFETs
+capable of making more advanced computers.
 
@@
 
+\begin{figure}[h]
+  \centering
+  \includegraphics[width = \linewidth]{images/41586_2018_770_Fig2_HTML.png}
+  \caption{MESO Spin Device Diagram illustrating various operating mechanisms (image from 
+  \cite{manipatruni2019scalable})}
+\end{figure}
+
 \subsubsection{Principle of Operation}
-An input logic is provided through a voltage and electric field which 
-will set the magnetization in a magnet to be in a certain direction. This 
-converts an electrical input into a magnetic state where the spin state 
-can now be used to represent the binary 0 or 1.
+The input logic is provided as an electrical charge or voltage. 
+This input is applied to a magnetoelectric switching node, which 
+can change the magnetization direction of the nanomagnet using a 
+voltage. This effectively converts the electrical input into a 
+stable magnetic state (representing a 0 or 1 based on its up or 
+down spin), which represents the logic state. This form of 
+"collective state switching" offers superior switching energy, 
+lower operating voltage, and enhanced logic density compared to 
+charge-only approaches.
 
-To then generate an output a current is injected into the nanomagnet 
-which will cause the output current from the nanomagnet to all have 
-the same
+The output logic is then generated by supplying a current into 
+the device. The magnetic state of the nanomagnet then determines 
+sets all the ejected electrons to be strongly polarized due to spin
+orbit coupling. This spin is then converted back into a charge 
+or voltage driving the subsequent logic gates.
+
+\subsubsection{Logic Implementation and Architecture}
+The key feature enabling logic implementation with MESO is due to 
+their ability to implement majority gates and inverters. MESO devices
+inherently suppport majority logic because of the way multiple 
+charge inputs can be summed together to influence the spin state
+of a nanomagnet. If the spin of the currents sum to be above a 
+certain threshold then that will be enough to change the spin state
+of the nanomagnet.
+
+An inverter can then be created by having a nanomagnet affect the 
+spin polarization of a wire. If a wire is placed close to a nanomagnet, 
+the nanomagnet will act as a sort of a filter. The nanomagnet 
+will affect the wire is such a way that electrons with the same spin 
+as the magnet will be attracted to the nanomagnet while electrons with 
+opposite spin are able to pass through. This then effectively 
+outputs a spin state that is opposite to the spin state of 
+the nanomagnet creating an inverter.
+
+These devices can then be cascaded together to perform more advanced 
+logic operations. While there still hasn't been much 
+substantial demonstration of this technology the theory is there 
+and complicated logic operations are definitely possible.
+\cite{manipatruni2019scalable}
+
+\subsection{Current Challenges in Spintronics}
+Despite the significant theoretical advantages of MESO devices, there 
+still stands considerable challengs to it's implementation. The primary 
+hurdle still lies in the fact that these devices cannot be produced reliably. 
+Temperature fluctuations also pose a significant threat to MESO devices
+as shifts in temperature can alter the spin states of the devices.
+
+\subsection{Personal Thoughts}
+While spintronics has a lot of promising benefits with its low power 
+and in memory compute, the possibility of an actual computer being 
+made with spintronics seems extremeley slim. The current state 
+that devices can be manufactured will be nowhere close to the 
+reliability needed for spintronics computers. Even in the case that 
+an actual computer can be made, it will definitely not be applicable 
+to home personal use due to the sensitivity of the devices and how easily 
+the spin could change.
+
+The operating principles behind spintronics inherently seems very
+volatile. Much like quantum computing, for it to be viable I think 
+extensive error correction algorithms will have to be used that will 
+take up a signficant amount of the compute available. The principles 
+also make it seem very difficult for the devices to be manufactured at 
+a scale comparable to current transistors. I think if spintronics 
+logic is to become a thing there may need to be different ways to 
+perform logic that is more robust and error tolerant and also perhaps 
+a bit more simple.
+
+There is also not much action if at all happening in industry 
+related to spintronics. Companies are still unwilling to invest 
+in which is a big indicator in how far off from deployment the 
+technology still is.
+
+Overall, I don't think spintronics will be very viable in performing 
+digital logic operations. It may have big potential in spaces like 
+memory, but just for logic I don't see it getting very far. If we don't 
+see any big advancements in the next 3-5 years I think the research 
+and investment around this technology will fall off and people 
+will invest all resources to quantum computing.
 
@@
 ability to store more than just 1 bit per device. Recent experiments
-have shown one memristor being able to store 5-7 bits. Advances 
+have shown one memristor being able to store 5-7 bits \cite{papandroulidakis2019practical}. Advances 
 in memristors have also demonstrated a high level of CMOS compatability 
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width = \linewidth]{images/Linearly_separable_red-blue_cropped_.svg.png}
+  \caption{Figure illustrating linearly separable function}
+\end{figure}
+
 \subsubsection{Memristor-Based Threshold Logic Gate}
@@
 whether the sum of the weights have surpassed the threshold. 
-%\cite here%
+\cite{papandroulidakis2019practical}
 
@@
 Fabrication is still very difficult and there are no EDA tools 
-compatible with designing devices made of memristors TLGs.
+compatible with designing devices made of memristors TLGs \cite{papandroulidakis2019practical}.
 
@@
 introduce nonlinearities, making the output resemble various desired 
-distributions. 
+distributions \cite{aguirre2024hardware}. 
 \begin{figure}[H]
   \centering
-  \includegraphics[scale = 0.3]{images/Neural-network-implementation-using-memristor-crossbar-arrays-a-shows-a-conventional.png}
-  \caption{Memristor crossbar array}
+  \includegraphics[width = \linewidth]{images/Neural-network-implementation-using-memristor-crossbar-arrays-a-shows-a-conventional.png}
+  \caption{Memristor crossbar array (image from \cite{hassan2018real})}
 \end{figure}
@@
 the cases as benign or malignant with 94.6\% accuracy.
-%cite here%
+\cite{cai2019fully}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width = \linewidth]{images/Screenshot 2025-06-07 at 8.22.50 PM.png}
+  \caption{Illustration of multiple advances achieved by UMich memristor computer (image from \cite{cai2019fully})}
+\end{figure}
 
@@
 \subsection{Personal Thoughts}
-With the advent of
+With the advent of AI and the need for massive amounts of compute 
+I see memristors having a big potential to fill this opportunity 
+to create more powerful and efficient asics for machine learning. 
+The development in recent years has also been pretty promising with 
+UMich demonstrating the memristor computer implementing a 
+single layer perceptron.
+
+There also seems to be quite a few startups in the space
+indicating that memristors may have gotten to the point where 
+industry is willing to invest in them. With all the AI startup 
+hype these companies are getting massive amounts of money 
+and it will boost these companies and the overall memristor fields 
+capability to make a breakthrough.
+
+Outside of making neural networks, I don't think memristors have 
+that much viability. The current methods for creating logic gates 
+with memristors need quite a lot of traditional CMOS technology to 
+support it that it just seems like too much effort for not enough 
+benefit. The in memory compute promise also doesn't look too strong
+yet and until there can be a way to store significant amounts of memory with 
+memristors in the compute block I don't see general purpose memristor 
+computers coming anytime soon.
 
 \section{Comparative Analysis}
+This section will then dive into my personal opinions on how these 
+technologies compare with each other weighing their respective 
+weaknesses and strengths, exploring potential synergies, and consider 
+the current landscape of compute and where money and effort is 
+being directed.
+
+The three technologies highlighted above are all among the most 
+researched post CMOS technologies in the past few decades. However, 
+some definitely have more promise than others. There can 
+only be a few winners, and inevitably some will have to fade away 
+while others will enjoy widespread adoption. So what exactly are the 
+technologies that stand out and in what fields do they have potential.
+
+First, I will go over which technology I don't think will have 
+widespread adoption. That technology would have to be spintronics. 
+The main appeal of spintronics is its ability to perform in memory compute. 
+This idea is definitely appealing as one of the main bottlenecks that now arise 
+scaling compute is the ability to move information to and from memory and compute. 
+Spintronics definitely does have its advantanges in this area, however I feel like 
+memristors also guarantee this promise in a much more simple and easily conceivable way.
+
+On the logic side, though spintronics does promise more capable logic abilities with 
+the potential of representing more than 2 states in a single bit, the implementation 
+just seems too complicated to become scalable. Of course it sounds nice to be able 
+to implement more states, but if you're not able to scale this than it's not really 
+of any use. Even if scalability is achieved the operating principles behind spintronics 
+logic like storing spin states in a nanomagnet are too volatile to be used in anything 
+outside of specialized supercomputers.
+
+On top of all this, the whole field didn't seem to have too many tangible achievements in 
+recent times. Research and theory is great, but if none of it can be turned into an actual 
+demonstrable product then it really is just theorizing. Unlike the other two technologies 
+that have all produced computers that have been able to accomplish some simple and basic tasks
+spintronics has not done any of this.
+
+The technology also doesn't appeal much to the landscape of the industry. With AI being 
+all the craze and where all the investment is going, spintroncis doesn't seemed to 
+be involved in any of it.
+
+Carbon nanotubes and memristors on the other hand have much more potential while also 
+demonstrating significant results already. Their respective strengths in creating 
+hyper-efficient transistors and enabling powerful in-memory computing align directly
+with the primary challenges and investment trends in the industry today, making them 
+the most compelling candidates to lead the post-CMOS era.
+
+Carbon nanotubes in particular are extremely promising. The benefits they can provide 
+are a huge advantage of the transistors we already have. Even though they don't 
+present a whole new computing paradigm they still amount to a significant improvement 
+in the ability to scale compute. Their ballistic transport properties also make them 
+very compelling as it presents ways to reduce power scaling, one of the main factors 
+limiting our ability to add more transistors on a chip.
+
+The results that have already been realized using CNFETs are nothing short of incredible. 
+With the MIT Medical Electronic Device Realization center already building a complete 
+16 bit computer the promise of carbon nanotubes is no longer just in theory. It is 
+knocking on the doorstep ready to take computing to the next step
+
+Because they are not a completely new computing paradigm that also makes it quite appealing. 
+With technologies like spintronics and memristors presenting completely new ways to compute
+the industry may become hesitant to switch and it will take a significant amount of effort
+for everyone to adopt to something so different. Carbon nanotubes on the other hand can operate
+just like normal transistors making the transition much more seamless. The difficulty then just 
+lies in the fabrication while the rest of the industry can stay more or less the same.
+
+Perhaps one of the most transformative advantages of carbon nanotubes is their potential 
+for true 3D integration. Unlike silicon, which requires high-temperature processing that 
+prevents stacking active layers, CNTs can be fabricated at low temperatures. This opens the 
+door to building processors vertically, layer by layer, leading to an unprecedented density
+of compute and memory interwoven in a single chip. This positions CNTs as the heir apparent 
+to silicon for processing tasks.
+
+Finally, memristors who don't have as much potential as carbon nanotubes in the world 
+of general have massive potential in the world of specialized AI chips. Their inherent 
+ability to do matrix multiplication makes them especially appealing in this day and age 
+where training the best AI is what has captivated governments around the world.
+
+Just like carbon nanotubes, the results that have already been shown using memristors have 
+been nothing short of incredible. The University of Michigan implmeneting a single layer 
+perceptron also demonstrates that memristors are also not just something of theory. If these 
+results can be demonstrated on progressively larger scale models then they have a serious 
+chance of taking over the AI industry and becoming the dominant way of making chips in
+that space.
+
+All of this is without even mentioning their potential for in memory compute. Just like 
+spintronics, they have the ability to combine memory and compute in the same module and 
+if this can be utilized in addition to their matrix multiplication then memristors also 
+have a potential chance of brekaing into the general compute space.
+
+While they are also still quite volatile, just like spintronics, the advancement of 
+memristors to become consistent and scalable seem much easier than nanomagnets. Carbon 
+nanotubes still stand a step above them in terms of reliability and scalability and are 
+ahead in manufacturing maturity.
+
+In the final analysis, the race to succeed CMOS may not produce a single winner, 
+but rather a new, specialized hierarchy of technologies. While spintronics appears to 
+be a distant prospect due to fundamental hurdles, the paths for carbon nanotubes and 
+memristors are becoming increasingly clear. Carbon nanotubes stand out as the most 
+pragmatic and powerful successor for general-purpose logic, promising to extend the 
+paradigm of Moore's Law through superior efficiency and 3D integration. They represent 
+the perfection of the processor as we know it.
+
+However, perfecting the processor alone is not enough. The future of computing, 
+particularly in the age of AI, hinges on solving the data bottleneck. This is where 
+memristors, with their profound potential for in-memory and analog computing, will 
+dominate. There is a possibility of a hybrid future where efficient logic chips built 
+from carbon nanotubes work in seamless integration with memristor based accelerators 
+and memory modules. Dividing the labor and letting each technology excel at its 
+inherents strengths present a logical and promising path forward.
 
 \section{Conclusion}
+The relentless march of progress in computing has driven 
+silicon-based CMOS technology to its fundamental physical limits, 
+necessitating a paradigm shift towards novel materials and 
+architectural approaches. This paper has explored three 
+cutting-edge technologies—Carbon Nanotubes (CNTs), Spintronics, 
+and Memristors—each offering distinct and powerful solutions to 
+the challenges of performance, power consumption, and 
+architectural bottlenecks inherent in current computing systems.
 
-\section{Acknowledgments}
+Carbon Nanotubes stand as a compelling successor to silicon in 
+transistor technology. Their nanoscale dimensions, exceptional 
+carrier mobility, and superior thermal properties enable the 
+creation of CNFETs that promise higher speeds, lower power 
+consumption, and greater scalability, as evidenced by the 
+development of functional CNFET-based microprocessors. While 
+significant fabrication hurdles related to material purity and 
+manufacturing uniformity remain, the ongoing advancements 
+underscore their potential to extend the capabilities of 
+traditional digital logic.
 
-Authors of any work published by ACM will need to complete a rights
-form. Depending on the kind of work, and the rights management choice
-made by the author, this may be copyright transfer, permission,
-license, or an OA (open access) agreement.
+Spintronics, by harnessing the intrinsic spin of electrons, 
+introduces a revolutionary approach to logic and memory. 
+Magnetoelectric Spin-Orbit (MESO) devices demonstrate the 
+ability to perform ultra-low-power logic operations by converting 
+charge to magnetic states and back, enabling efficient information 
+processing with minimal energy dissipation. The inherent 
+capability to implement majority gates and inverters fundamentally 
+redefines logic design, paving the way for highly dense and 
+energy-efficient circuits. Overcoming challenges in gate 
+reliability and material integration will be crucial for 
+widespread adoption.
 
-Regardless of the rights management choice, the author will receive a
-copy of the completed rights form once it has been submitted. This
-form contains \LaTeX\ commands that must be copied into the source
-document. When the document source is compiled, these commands and
-their parameters add formatted text to several areas of the final
-document:
-\begin{itemize}
-\item the ``ACM Reference Format'' text on the first page.
-\item the ``rights management'' text on the first page.
-\item the conference information in the page header(s).
-\end{itemize}
+Finally, Memristors present a transformative solution to the 
+enduring Von Neumann bottleneck by merging memory and processing 
+capabilities within a single device. Their unique properties, 
+including nanoscale dimensions, non-volatility, and multi-bit 
+storage, make them ideal for neuromorphic computing and in-memory 
+acceleration of Artificial Neural Networks. The successful 
+implementation of memristor-based threshold logic gates and 
+complex neural networks showcases their profound potential to 
+enable highly efficient, brain-inspired architectures, despite 
+ongoing challenges in manufacturing consistency and programming 
+precision.
 
-Rights information is unique to the work; if you are preparing several
-works for an event, make sure to use the correct set of commands with
-each of the works.
-
-The ACM Reference Format text is required for all articles over one
-page in length, and is optional for one-page articles (abstracts).
-
-\section{CCS Concepts and User-Defined Keywords}
-
-Two elements of the ``acmart'' document class provide powerful
-taxonomic tools for you to help readers find your work in an online
-search.
-
-The ACM Computing Classification System ---
-\url{https://www.acm.org/publications/class-2012} --- is a set of
-classifiers and concepts that describe the computing
-discipline. Authors can select entries from this classification
-system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
-commands to be included in the \LaTeX\ source.
-
-User-defined keywords are a comma-separated list of words and phrases
-of the authors' choosing, providing a more flexible way of describing
-the research being presented.
-
-CCS concepts and user-defined keywords are required for for all
-articles over two pages in length, and are optional for one- and
-two-page articles (or abstracts).
-
-\section{Sectioning Commands}
-
-Your work should use standard \LaTeX\ sectioning commands:
-\verb|\section|, \verb|\subsection|, \verb|\subsubsection|,
-\verb|\paragraph|, and \verb|\subparagraph|. The sectioning levels up to
-\verb|\subsusection| should be numbered; do not remove the numbering
-from the commands.
-
-Simulating a sectioning command by setting the first word or words of
-a paragraph in boldface or italicized text is {\bfseries not allowed.}
-
-Below are examples of sectioning commands.
-
-\subsection{Subsection}
-\label{sec:subsection}
-
-This is a subsection.
-
-\subsubsection{Subsubsection}
-\label{sec:subsubsection}
-
-This is a subsubsection.
-
-\paragraph{Paragraph}
-
-This is a paragraph.
-
-\subparagraph{Subparagraph}
-
-This is a subparagraph.
-
-\section{Tables}
-
-The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
-package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
-high-quality tables.
-
-Table captions are placed {\itshape above} the table.
-
-Because tables cannot be split across pages, the best placement for
-them is typically the top of the page nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and the
-table caption.  The contents of the table itself must go in the
-\textbf{tabular} environment, to be aligned properly in rows and
-columns, with the desired horizontal and vertical rules.  Again,
-detailed instructions on \textbf{tabular} material are found in the
-\textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table~\ref{tab:freq} is included in the input file; compare the
-placement of the table here with the table in the printed output of
-this document.
-
-\begin{table}
-  \caption{Frequency of Special Characters}
-  \label{tab:freq}
-  \begin{tabular}{ccl}
-    \toprule
-    Non-English or Math&Frequency&Comments\\
-    \midrule
-    \O & 1 in 1,000& For Swedish names\\
-    $\pi$ & 1 in 5& Common in math\\
-    \$ & 4 in 5 & Used in business\\
-    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-  \bottomrule
-\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of the page's
-live area, use the environment \textbf{table*} to enclose the table's
-contents and the table caption.  As with a single-column table, this
-wide table will ``float'' to a location deemed more
-desirable. Immediately following this sentence is the point at which
-Table~\ref{tab:commands} is included in the input file; again, it is
-instructive to compare the placement of the table here with the table
-in the printed output of this document.
-
-\begin{table*}
-  \caption{Some Typical Commands}
-  \label{tab:commands}
-  \begin{tabular}{ccl}
-    \toprule
-    Command &A Number & Comments\\
-    \midrule
-    \texttt{{\char'134}author} & 100& Author \\
-    \texttt{{\char'134}table}& 300 & For tables\\
-    \texttt{{\char'134}table*}& 400& For wider tables\\
-    \bottomrule
-  \end{tabular}
-\end{table*}
-
-Always use midrule to separate table header rows from data rows, and
-use it only for this purpose. This enables assistive technologies to
-recognise table headers and support their users in navigating tables
-more easily.
-
-\section{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of the three are
-discussed in the next sections.
-
-\subsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an inline or
-in-text formula.  It is produced by the \textbf{math} environment,
-which can be invoked with the usual
-\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
-the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
-and structures, from $\alpha$ to $\omega$, available in
-\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
-examples of in-text equations in context. Notice how this equation:
-\begin{math}
-  \lim_{n\rightarrow \infty}x=0
-\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsection{Display Equations}
-A numbered display equation---one set off by vertical space from the
-text and centered horizontally---is produced by the \textbf{equation}
-environment. An unnumbered display equation is produced by the
-\textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols and
-structures available in \LaTeX\@; this section will just give a couple
-of examples of display equations in context.  First, consider the
-equation, shown as an inline equation above:
-\begin{equation}
-  \lim_{n\rightarrow \infty}x=0
-\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}
-  \sum_{i=0}^{\infty} x + 1
-\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}
-  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
-\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\section{Figures}
-
-The ``\verb|figure|'' environment should be used for figures. One or
-more images can be placed within a figure. If your figure contains
-third-party material, you must clearly identify it as such, as shown
-in the example below.
-\begin{figure}[h]
-  \centering
-%   \includegraphics[width=\linewidth]{sample-franklin}
-  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
-    Ewing, Inc. [Public domain], via Wikimedia
-    Commons. (\url{https://goo.gl/VLCRBB}).}
-  \Description{A woman and a girl in white dresses sit in an open car.}
-\end{figure}
-
-Your figures should contain a caption which describes the figure to
-the reader.
-
-Figure captions are placed {\itshape below} the figure.
-
-Every figure should also have a figure description unless it is purely
-decorative. These descriptions convey what’s in the image to someone
-who cannot see it. They are also used by search engine crawlers for
-indexing images, and when images cannot be loaded.
-
-A figure description must be unformatted plain text less than 2000
-characters long (including spaces).  {\bfseries Figure descriptions
-  should not repeat the figure caption – their purpose is to capture
-  important information that is not already provided in the caption or
-  the main text of the paper.} For figures that convey important and
-complex new information, a short text description may not be
-adequate. More complex alternative descriptions can be placed in an
-appendix and referenced in a short figure description. For example,
-provide a data table capturing the information in a bar chart, or a
-structured list representing a graph.  For additional information
-regarding how best to write figure descriptions and why doing this is
-so important, please see
-\url{https://www.acm.org/publications/taps/describing-figures/}.
-
-\subsection{The ``Teaser Figure''}
-
-A ``teaser figure'' is an image, or set of images in one figure, that
-are placed after all author and affiliation information, and before
-the body of the article, spanning the page. If you wish to have such a
-figure in your article, place the command immediately before the
-\verb|\maketitle| command:
-\begin{verbatim}
-  \begin{teaserfigure}
-    \includegraphics[width=\textwidth]{sampleteaser}
-    \caption{figure caption}
-    \Description{figure description}
-  \end{teaserfigure}
-\end{verbatim}
-
-\section{Citations and Bibliographies}
-
-The use of \BibTeX\ for the preparation and formatting of one's
-references is strongly recommended. Authors' names should be complete
---- use full first names (``Donald E. Knuth'') not initials
-(``D. E. Knuth'') --- and the salient identifying features of a
-reference should be included: title, year, volume, number, pages,
-article DOI, etc.
-
-The bibliography is included in your source document with these two
-commands, placed just before the \verb|\end{document}| command:
-\begin{verbatim}
-  \bibliographystyle{ACM-Reference-Format}
-  \bibliography{bibfile}
-\end{verbatim}
-where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
-suffix, of the \BibTeX\ file.
-
-Citations and references are numbered by default. A small number of
-ACM publications have citations and references formatted in the
-``author year'' style; for these exceptions, please include this
-command in the {\bfseries preamble} (before the command
-``\verb|\begin{document}|'') of your \LaTeX\ source:
-\begin{verbatim}
-  \citestyle{acmauthoryear}
-\end{verbatim}
-
-  Some examples.  A paginated journal article \cite{Abril07}, an
-  enumerated journal article \cite{Cohen07}, a reference to an entire
-  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
-  monograph/whole book in a series (see 2a in spec. document)
-  \cite{Harel79}, a divisible-book such as an anthology or compilation
-  \cite{Editor00} followed by the same example, however we only output
-  the series if the volume number is given \cite{Editor00a} (so
-  Editor00a's series should NOT be present since it has no vol. no.),
-  a chapter in a divisible book \cite{Spector90}, a chapter in a
-  divisible book in a series \cite{Douglass98}, a multi-volume work as
-  book \cite{Knuth97}, a couple of articles in a proceedings (of a
-  conference, symposium, workshop for example) (paginated proceedings
-  article) \cite{Andler79, Hagerup1993}, a proceedings article with
-  all possible elements \cite{Smith10}, an example of an enumerated
-  proceedings article \cite{VanGundy07}, an informally published work
-  \cite{Harel78}, a couple of preprints \cite{Bornmann2019,
-    AnzarootPBM14}, a doctoral dissertation \cite{Clarkson85}, a
-  master's thesis: \cite{anisi03}, an online document / world wide web
-  resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game
-  (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05}
-  and (Case 3) a patent \cite{JoeScientist001}, work accepted for
-  publication \cite{rous08}, 'YYYYb'-test for prolific author
-  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
-  contain 'duplicate' DOI and URLs (some SIAM articles)
-  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
-  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
-  couple of citations with DOIs:
-  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
-  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}.
-  Artifacts: \cite{R} and \cite{UMassCitations}.
-
-\section{Acknowledgments}
-
-Identification of funding sources and other support, and thanks to
-individuals and groups that assisted in the research and the
-preparation of the work should be included in an acknowledgment
-section, which is placed just before the reference section in your
-document.
-
-This section has a special environment:
-\begin{verbatim}
-  \begin{acks}
-  ...
-  \end{acks}
-\end{verbatim}
-so that the information contained therein can be more easily collected
-during the article metadata extraction phase, and to ensure
-consistency in the spelling of the section heading.
-
-Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.
-
-\section{Appendices}
-
-If your work needs an appendix, add it before the
-``\verb|\end{document}|'' command at the conclusion of your source
-document.
-
-Start the appendix with the ``\verb|appendix|'' command:
-\begin{verbatim}
-  \appendix
-\end{verbatim}
-and note that in the appendix, sections are lettered, not
-numbered. This document has two appendices, demonstrating the section
-and subsection identification method.
-
-\section{Multi-language papers}
-
-Papers may be written in languages other than English or include
-titles, subtitles, keywords and abstracts in different languages (as a
-rule, a paper in a language other than English should include an
-English title and an English abstract).  Use \verb|language=...| for
-every language used in the paper.  The last language indicated is the
-main language of the paper.  For example, a French paper with
-additional titles and abstracts in English and German may start with
-the following command
-\begin{verbatim}
-\documentclass[sigconf, language=english, language=german,
-               language=french]{acmart}
-\end{verbatim}
-
-The title, subtitle, keywords and abstract will be typeset in the main
-language of the paper.  The commands \verb|\translatedXXX|, \verb|XXX|
-begin title, subtitle and keywords, can be used to set these elements
-in the other languages.  The environment \verb|translatedabstract| is
-used to set the translation of the abstract.  These commands and
-environment have a mandatory first argument: the language of the
-second argument.  See \verb|sample-sigconf-i13n.tex| file for examples
-of their usage.
-
-\section{SIGCHI Extended Abstracts}
-
-The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
-not in Word) produces a landscape-orientation formatted article, with
-a wide left margin. Three environments are available for use with the
-``\verb|sigchi-a|'' template style, and produce formatted output in
-the margin:
-\begin{description}
-\item[\texttt{sidebar}:]  Place formatted text in the margin.
-\item[\texttt{marginfigure}:] Place a figure in the margin.
-\item[\texttt{margintable}:] Place a table in the margin.
-\end{description}
+In conclusion, while each of these technologies faces its own set 
+of engineering and scientific challenges, their combined potential
+is immense. They offer not just incremental improvements but 
+pathways to fundamentally reshape how information is processed 
+and stored. Whether through the direct performance enhancement of 
+CNFETs, the ultra-low-power logic of spintronics, or the 
+architectural revolution promised by memristors, the future of 
+computing will undoubtedly be a fascinating interplay of these 
+emerging paradigms, leading to more intelligent, efficient, and 
+powerful computational systems.
 
@@
 \begin{acks}
-To Robert, for the bagels and explaining CMYK and color spaces.
+This work would not have been possible without the support of Professor Srivastava. None of this paper could 
+have come together without your mentorship. Thank you for giving me the opportunity to
+research this topic as well. Without this class, I would have never read into this field with such 
+depth and it has truly provided me with some valuable insight in addition to skills on 
+how to read and analyze papers.
+
+Of course, this paper would also not have been possible without my classmates. I can say 
+confidently that my paper would be nowhere near where it is now had it not 
+been for my classmates support and comradery. I have also learned so much through 
+each of their presentations. 
 \end{acks}
@@
 
-%%
-%% If your work has an appendix, this is the place to put it.
-\appendix
-
-\section{Research Methods}
-
-\subsection{Part One}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
-malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
-sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
-vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
-lacinia dolor. Integer ultricies commodo sem nec semper.
-
-\subsection{Part Two}
-
-Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
-ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
-ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
-eros. Vivamus non purus placerat, scelerisque diam eu, cursus
-ante. Etiam aliquam tortor auctor efficitur mattis.
-
-\section{Online Resources}
-
-Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
-pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
-enim maximus. Vestibulum gravida massa ut felis suscipit
-congue. Quisque mattis elit a risus ultrices commodo venenatis eget
-dui. Etiam sagittis eleifend elementum.
-
-Nam interdum magna at lectus dignissim, ac dignissim lorem
-rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
-massa et mattis lacinia.
-
 \end{document}

### 2025-06-14 Paper.tex
finish 2

@@
   systems for the next generation.
-  CMOS.
 \end{abstract}
@@
 metal-oxide-semiconductor) technology has served as the foundation 
-of of the modern computer. However, as we continue to approve our 
+of the modern computer. However, as we continue to improve our 
 transistors and approach fundamental limits, the need for novel 
-paradigms becomes increasinly urgent. This paper explores three 
+paradigms becomes increasingly urgent. This paper explores three 
 technologies that could shape the future of computing: Carbon Nanotubes
-(CNTs), Spintronics, and Memristors. Each offers their own 
+(CNTs), Spintronics, and Memristors. Each offers its own 
 advantages that address the limitations of silicon transistors,
@@
 \section{Carbon Nanotubes (CNTs) for Advanced Electronics}
-As the semiconductor continues its pursuit of miniaturization 
+As the semiconductor industry continues its pursuit of miniaturization 
 and greater performance, the fundamental limits of silicon-based 
@@
 with their structure determining whether they behave as
-semiconductors or metals. his tunable electrical property,
+semiconductors or metals. This tunable electrical property,
 coupled with their nanoscale dimensions, 
@@
 
-Their structure can be characterized into to major types.
+Their structure can be characterized into two major types.
 Single-walled and multi-walled carbon nanotubes. Single-walled 
@@
 to process and store information. 1s and 0s are coded by high and 
-low volages which are determined by electric fields created by
+low voltages which are determined by electric fields created by
 distributions of charges. However, this approach faces inherent 
@@
 devices continue to shrink. Spintronics emerges as a new paradigm 
-that seeks to overcome these limitations by exploiting not only electron's 
+that seeks to overcome these limitations by exploiting not only the electron's 
 charge but also its intrinsic angular momentum, known as spin. 
@@
 operations with significantly reduced energy footprints. 
-By also utilizing using a charge as well as spin this gives the potential to encode more 
+By also using a charge as well as spin this gives the potential to encode more 
 states where there can be a combination of high or low voltage along 
@@
 and in memory compute, the possibility of an actual computer being 
-made with spintronics seems extremeley slim. The current state 
+made with spintronics seems extremely slim. The current state 
 that devices can be manufactured will be nowhere close to the 
@@
 A memristor, combination of the words memory and resistor, is a device 
-that can have a programmble resistance. It was often described as 
+that can have a programmable resistance. It was often described as 
 the fourth circuit element because it was believed that magnetic fields 
@@
 of voltages from 0-9 and there is a threshold voltage of 5. Any
-input voltage above high will output a binary high signal from the 
+input voltage above the threshold will output a binary high signal from the 
 gate and any voltage below will output a low signal. A TLG 
@@
 The central component in the vector-matrix multiplication core 
-is the memristor crossbar array. In this array, memrisotrs are placed
+is the memristor crossbar array. In this array, memristors are placed
 at the crosspoints of a grid of wires. Voltages are inputted through
@@
 in how the resistance is programmed also make it extremely difficult to
-program large scale memristor arrays. Supposed identitical memristors 
+program large scale memristor arrays. Supposedly identitical memristors 
 could require different voltage thresholds or to be applied for varying 
@@
 The technology also doesn't appeal much to the landscape of the industry. With AI being 
-all the craze and where all the investment is going, spintroncis doesn't seemed to 
+all the craze and where all the investment is going, spintronics doesn't seem to 
 be involved in any of it.
@@
 Just like carbon nanotubes, the results that have already been shown using memristors have 
-been nothing short of incredible. The University of Michigan implmeneting a single layer 
+been nothing short of incredible. The University of Michigan implementing a single layer 
 perceptron also demonstrates that memristors are also not just something of theory. If these 
@@
 if this can be utilized in addition to their matrix multiplication then memristors also 
-have a potential chance of brekaing into the general compute space.
+have a potential chance of breaking into the general compute space.
 
@@
 and memory modules. Dividing the labor and letting each technology excel at its 
-inherents strengths present a logical and promising path forward.
+inherent strengths present a logical and promising path forward.
 
@@
 \begin{acks}
-This work would not have been possible without the support of Professor Srivastava. None of this paper could 
-have come together without your mentorship. Thank you for giving me the opportunity to
+This work would not have been possible without the support of Professor Srivastava. This paper could not have come together without your mentorship. Thank you for giving me the opportunity to
 research this topic as well. Without this class, I would have never read into this field with such 
@@
 confidently that my paper would be nowhere near where it is now had it not 
-been for my classmates support and comradery. I have also learned so much through 
+been for my classmates' support and comradery. I have also learned so much through 
 each of their presentations. 
